---
title: "WriteUp-Linear-Model-with-prediction"
author: "Anthony Falconio"
date: "Fall 2023"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
---


```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```

```{r, eval=TRUE,warning=FALSE}
url <- "https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt"
mydata <- read.csv(file=url,sep="",header=TRUE)
```

##Introduction

After looking at the data from RVLS on the physical strength and job performance of workers. We want to compare the numerical data called SIMS with the arm, grip, and arm+grip variables to see if there is a correlation in the data between the numerical variables.

$H_0$ There is no correlation between the numerical variables

$H_A$ There is a significant correlation between the numerical variables according to the data

##Methods

```{r}
glimpse(mydata)
model1 <- lm(SIMS~ARM,data=mydata)
model2 <- lm(SIMS~GRIP,data=mydata)
model3 <- lm(SIMS~ARM+GRIP,data=mydata)
sims <- mean(mydata$SIMS)
target1 <- data.frame(ARM=88,GRIP=94)
```
From looking at the environment tab, we can see that we will be comparing numerical variables which will likely include the use of the CandP helper files as this is a num~num problem. We will look at the data using scatter plots and a linear regression model.

## Graphical Results

```{r include = TRUE, echo = FALSE,}
ggplot(mydata, aes(x = ARM, y= SIMS))+
  geom_smooth(method=lm)+
  geom_point()+
  labs(x = "ARMS", y = "SIMS") +
  ggtitle("Scatterplot of ARMS vs. SIMS")

ggplot(mydata, aes(x = GRIP, y= SIMS))+
  geom_smooth(method=lm)+
  geom_point()+
  labs(x = "GRIP", y = "SIMS") +
  ggtitle("Scatterplot of GRIP vs. SIMS")

ggplot(mydata, aes(x = ARM+GRIP, y= SIMS))+
  geom_smooth(method=lm)+
  geom_point()+
  labs(x = "ARMS+GRIP", y = "SIMS") +
  ggtitle("Scatterplot of ARMS+GRIP vs. SIMS")
```

Just from looking at the scatter plots, we can tell that there is positive relationship  with all three variables including ARM, GRIP, and ARM+GRIP, but numerical and inferential results will allow us to analyze the data from a numerical standpoint.

## Numerical Results
```{r}
cor(SIMS~ARM,data=mydata)
cor(SIMS~GRIP,data=mydata)
cor(SIMS~ARM+GRIP,data=mydata)
```

From looking at the correlation in the three models, we can see that the third model has the strongest correlation of ARM+GRIP, followed by ARM, and then GRIP with the weakest correlation.


##Inferential Results
```{r, include=TRUE, echo = FALSE}
cat("Model 1")
summary.lm(model1)
predict(model1,target1,interval=c("prediction"))
cat("4.8 = Difference")

cat("Model 2")
summary.lm(model2)
predict(model2,target1,interval=c("prediction"))
cat("5.2 = Difference")

cat("Model 3")
summary.lm(model3)
predict(model3,target1,interval=c("prediction"))
cat("4.6 = Difference")
```



```{r, include = TRUE, echo = FALSE}
cat("Model 1 & 2 ")
anova(model1,model2)
cat("\n\n\n Model 2 & 3 ")
anova(model2,model3)
cat("\n\n\n Model 1 & 3 ")
anova(model1,model3)
```




